APPM 3310 Project\\\Large{Static Analysis of Truss Systems}

### 2016-04-28 paper.tex
Add figures and fixes.

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{listings}

@@

@@

@@

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{float}

@@

\begin{figure}[H]
    \begin{center}
        \includegraphics[width=0.8\textwidth]{images/sample_001.pdf}
        \caption{Truss Analyzer on a single truss member with one external
        force.}
    \end{center}
\end{figure}

\begin{figure}[H]
    \begin{center}
        \includegraphics[width=1\textwidth]{images/baltimore_truss.pdf}
        \caption{The DSM application of FEM on a much more complicated system
        (a Baltimore truss bridge) with 11 applied forces. This example
        clearly depicts the practical power of such analysis.}
    \end{center}
\end{figure}

\begin{figure}[H]
    \begin{center}
        \includegraphics[width=0.8\textwidth]{images/sample_002.pdf}
        \caption{3D analysis of a single truss with one applied force in the
        same plane as the truss system.}
    \end{center}
\end{figure}

\begin{figure}[H]
    \begin{center}
        \includegraphics[width=0.8\textwidth]{images/sample_003.pdf}
        \caption{The DSM application of FEM on a full three dimensional truss
        with multiple forces in three dimensions.}
    \end{center}
\end{figure}

\begin{figure}[H]
    \begin{center}
        \includegraphics[width=0.8\textwidth]{images/sample_004.pdf}
        \caption{The DSM application of FEM on an overconstrained truss
        system.}
    \end{center}
\end{figure}

@@

Truss analysis using DSM ignores many real world phenomena and has many
limitations in terms of complexity for the sake of simplicity. A more
realistic, yet much more complicated FEM tool could be created to analyze a
truss system taking into account more real world phenomena and allowing for
much more information to be imputed about the truss system. For example we
assume all nodes or joints, are connected by a pin joint. Such is not true for
many bridges, as they may be connected with gusset plates or may be non rigid
cables. The simplifications and assumptions that are made by the truss
analyzer are as follows: friction is ignored, the bending of truss members is
ignored, the cross sectional area of each truss element is assumed to be
constant, nodes do not impart torque on elements, and forces can only be
applied at nodes. On the flip side, our simple truss analyzer is powerful in
the way that it can solve both 2D and 3D truss systems, although manual
implementation of the input code would be extremely tedious for 3D systems.

@@

The truss analyzer is able to properly analyze a complex truss system based on
three known values: forces, displacements, and elastic moduli. Using
calculations based on these values and structure geometry. The script is able
to break down a truss system and implement the DSM by idealizing the truss
system, and simplifying complex real world phenomena into a manageable set of
linear stiffness equations. These stiffness equations are used to describe the
structure's elements, each of which can be subjected to an external force and
a displacement at a node. From this, a global stiffness matrix is created and
solved using the force vectors and displacement vectors. This DSM truss
analysis can be used for complex truss structures, for a very preliminary
design analysis. Solving for the stresses on these nodes without the use of
linear algebra is nearly impossible and/or extremely tedious. Through this DSM
analysis, using linear algebraic methods, more complex structures, notably:
bridges, wings, buildings, can be analyzed. Knowing the stresses on elements
of these structures allows engineers to predict behavior of structures under
force. Such behaviors that can be predicted are elastic deformation, plastic
deformation, crack growth, crack propagation, and structural failure, from
this it is easy to see why such structure analysis is important.
